Tutorial: Quantifying Spatially Resolved Hydration Thermodynamics Using Grid Inhomogeneous Solvation Theory [Article v\versionnumber]

### 2024-07-01 manuscript/manuscript.tex
Update to figure 6
Split figure into two visualisations, one for energy and one for entropy

\usepackage{listings}
\usepackage{upquote}
\usepackage{tabularx}

@@

\begin{lstlisting}[style=pymol]
load output/streptavidin/gist.pdb, streptavidin
as surface
color gray70, streptavidin
load output/streptavidin/gist-gO.dx, gO
isomesh gO_high, gO, 2
color slate, gO_high
\end{lstlisting}
A more sophisticated visualization, including the energy, entropy, and free energy of removing a single water solvent molecule, is found in Figure~\ref{fig-binding-pocket.png}

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{figures/binding-pocket-energy-levels.png}
	\caption{Biotin in the streptavidin binding pocket, with isosurfaces based on the GIST calculation on the holo structure. 
	Blue: negative entropy ($T\Delta S$). Green: negative energy (based on $E_{sw} + 2E_{ww}$). Red: positive energy. 
	Isolevels are ($\pm$) 0.25, 0.5, 1.0, 1.5, 2.0, 2.5, and 3.0 \si{\kcal\per\mole\per\angstrom\squared}, except for the 
	positive energy, where they are divided by 
	two.}\label{fig-binding-pocket.png}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=1.0\linewidth]{figures/streptavidin_gO_high_surf.png}
	\caption{Oxygen density around streptavidin at an isolevel of twice the reference density}\label{fig-streptavidin_gO}
\end{figure}

>>>>

\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{upquote}
\usepackage{tabularx}

@@

\begin{lstlisting}[style=pymol]
load output/streptavidin/gist.pdb, streptavidin
as surface
color gray70, streptavidin
load output/streptavidin/gist-gO.dx, gO
isomesh gO_high, gO, 2
color slate, gO_high
\end{lstlisting}
A more sophisticated visualization, including the energy, entropy, and free energy of removing a single water solvent 
molecule, is found in Figure~\ref{fig-binding-pocket}

\begin{figure}
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
	\includegraphics[width=\linewidth]{figures/binding-pocket-E.png}
	\caption{Green: negative energy (based on $E_{sw} + 2E_{ww}$). Red: positive energy.}
	\label{fig-binding-pocket-energy}
    \end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.3\textwidth}
		\includegraphics[width=\linewidth]{figures/binding-pocket-S.png}
		\caption{Blue: negative entropy}
		\label{fig-binding-pocket-entropy}
	\end{subfigure}
	\caption{Biotin in the streptavidin binding pocket, with isosurfaces based on the GIST calculation on the holo structure. 
	Isolevels shown are ($\pm$) 0.25, 0.5, 1.0, 1.5, 2.0, 2.5, and 3.0 \si{\kcal\per\mole\per\angstrom\square}, except for 
	the positive energy, where they are divided by two.}
	\label{fig-binding-pocket}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=1.0\linewidth]{figures/streptavidin_gO_high_surf.png}
	\caption{Oxygen density around streptavidin at an isolevel of twice the reference density}
	\label{fig-streptavidin_gO}
\end{figure}
